---
title: "Repaired_Seq_Activity" ## KCL KCL low KCL+pki pki and low TTX == Activity mask
output: html_document
---
```{r}
library("DiffBind")
library("ChIPpeakAnno")
library("ChIPseeker")
library("pqsfinder")
library("motifRG")
library("BSgenome.Hsapiens.UCSC.hg38")
library("EnsDb.Hsapiens.v86")
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("clusterProfiler")
library("ReactomePA")
library("org.Hs.eg.db")
library("viridis")
library("ggplot2")
library("ggExtra")
library("ggmisc")

txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene
anno86 <- annoGR(EnsDb.Hsapiens.v86)

```

```{r}
### Load new dba and bcb objects.
load("repairseq_dbaV2.rdata")
#load("repairseq_bcbV2.rda")

###Add PARP

# New masks basic 1D Peaks Common across H1 and H9
dba_H1H9_mask <- dba.mask(DBAobject,DBA_ID, c("H1","H9"))
dba_EdU_mask <- dba.mask(DBAobject,DBA_CONDITION, "EdU", mask=dba_H1H9_mask, merge="and")
dba_EdU_1Day_mask <- dba.mask(DBAobject,DBA_FACTOR,"1Day",mask=dba_EdU_mask, merge="and")
dba_EdU_1Day_KCl_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("KCl","None"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_KCl_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_KCl_mask, merge="and")
dba_1Day_EdU_KCl_ESCin <- dba(DBAobject,dba_EdU_1Day_KCl_ESCin_mask)
dba_KCl <- dba.contrast(dba_1Day_EdU_KCl_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_KCl <- dba.analyze(dba_KCl, method=DBA_DESEQ2)
#Peaks gained by KCL treatment
dba_KCl_Report <- dba.report(dba_KCl, contrast=1, th=1, bUsePval=TRUE, bCounts = TRUE, bFlip = TRUE)

df_KCl_vs_None <- data.frame(dba_KCl_Report)

KCl_OE <- df_KCl_vs_None$FDR <= 0.05 

df_KCl_vs_None$threshold <- KCl_OE 
my_Colors <- c("#662d91","#1d8348")

pdf("KCl_vs_EdU.pdf")
ggplot(df_KCl_vs_None) +
        geom_point(aes(x=Fold, y=-log10(FDR), colour=threshold),size=1, shape=16) +
        ggtitle("KCl vs EdU") +
        xlab("log2 fold change") + 
        ylab("-log10 FDR") +
        #scale_y_continuous(limits = c(0,50)) +
        theme(legend.position = "none") + theme_classic() + scale_color_manual(values=my_Colors) + xlim(-5,5)

dev.off()

dba_KCL_gained <- dba_KCl_Report[dba_KCl_Report$Fold > 0 & dba_KCl_Report$FDR < .05]
dba_KCL_gained_df <- data.frame(dba_KCL_gained)
peakAnno_KCL_gained <- annotatePeak(dba_KCL_gained, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakAnno_KCL_gained_df <- data.frame(peakAnno_KCL_gained)
write.csv(peakAnno_KCL_gained_df, file="peakAnno_KCL_gained.csv")

dba_KCL_lost <- dba_KCl_Report[dba_KCl_Report$Fold < 0 & dba_KCl_Report$FDR < .05]
dba_KCL_lost_df <- data.frame(dba_KCL_lost)
peakAnno_KCL_lost <- annotatePeak(dba_KCL_lost, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakAnno_KCL_lost_df <- data.frame(peakAnno_KCL_lost)
write.csv(peakAnno_KCL_lost_df, file="peakAnno_KCL_lost.csv")


```

```{r}


dba_EdU_1Day_KCl.Pki_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("KCl_Pki","KCl"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_KCl.Pki_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_KCl.Pki_mask, merge="and")
dba_1Day_EdU_KCl.Pki_ESCin <- dba(DBAobject,dba_EdU_1Day_KCl.Pki_ESCin_mask)
dba_KCl.Pki <- dba.contrast(dba_1Day_EdU_KCl.Pki_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_KCl.Pki <- dba.analyze(dba_KCl.Pki, method=DBA_DESEQ2)
#Peaks lost with KCL + pKi
dba_KCl.Pki_Report <- dba.report(dba_KCl.Pki, contrast=1, th=1, bUsePval=TRUE, fold=1, bCounts = TRUE)


df_KCl.Pki_vs_KCl <- data.frame(dba_KCl.Pki_Report)

KCl.Pki_OE <- df_KCl.Pki_vs_KCl$FDR <= 0.05 

df_KCl.Pki_vs_KCl$threshold <- KCl.Pki_OE 
my_Colors <- c("#662d91","#1d8348")

pdf("KCl.Pki_vs_KCl.pdf")
ggplot(df_KCl.Pki_vs_KCl) +
        geom_point(aes(x=Fold, y=-log10(FDR), colour=threshold),size=1, shape=16) +
        ggtitle("KCl.Pki vs KCl") +
        xlab("log2 fold change") + 
        ylab("-log10 FDR") +
        #scale_y_continuous(limits = c(0,50)) +
        theme(legend.position = "none") + theme_classic() + scale_color_manual(values=my_Colors) + xlim(-7,7)

dev.off()

dba_KCL.Pki_gained <- dba_KCl.Pki_Report[dba_KCl.Pki_Report$Fold > 0 & dba_KCl.Pki_Report$FDR < .05]
dba_KCL.Pki_gained_df <- data.frame(dba_KCL.Pki_gained)
peakAnno_KCL.Pki_gained <- annotatePeak(dba_KCL.Pki_gained, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakAnno_KCL.Pki_gained_df <- data.frame(peakAnno_KCL.Pki_gained)
write.csv(peakAnno_KCL.Pki_gained_df, file="peakAnno_KCL.Pki_gained.csv")

dba_KCL.Pki_lost <- dba_KCl.Pki_Report[dba_KCl.Pki_Report$Fold < 0 & dba_KCl.Pki_Report$FDR < .05]
dba_KCL.Pki_lost_df <- data.frame(dba_KCL.Pki_lost)
peakAnno_KCL.Pki_lost <- annotatePeak(dba_KCL.Pki_lost, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakAnno_KCL.Pki_lost_df <- data.frame(peakAnno_KCL.Pki_lost)
write.csv(peakAnno_KCL.Pki_lost_df, file="peakAnno_KCL.Pki_lost.csv")


peakAnno_RPKMs <- annotatePeak(rpkm_gr, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")

peakanno_rpkm_df <- data.frame(peakAnno_RPKMs)

rpkm_promoters <- peakanno_rpkm_df[peakanno_rpkm_df$annotation == 'Promoter (<=1kb)',]
```

```{r}

# New masks basic 1D Peaks Common across H1 and H9
dba_H1H9_mask <- dba.mask(DBAobject,DBA_ID, c("H1","H9"))
dba_EdU_mask <- dba.mask(DBAobject,DBA_CONDITION, "EdU", mask=dba_H1H9_mask, merge="and")
dba_EdU_1Day_mask <- dba.mask(DBAobject,DBA_FACTOR,"1Day",mask=dba_EdU_mask, merge="and")
dba_EdU_1Day_KCl_TTX_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("KCl","None","TTX_low"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_KCl_TTX_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_KCl_TTX_mask, merge="and")
dba_1Day_EdU_KCl_TTX_ESCin <- dba(DBAobject,dba_EdU_1Day_KCl_TTX_ESCin_mask)
dba_KCl_All <- dba.contrast(dba_1Day_EdU_KCl_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_KCl_All <- dba.analyze(dba_KCl_All, method=DBA_DESEQ2)
#Peaks gained by KCL treatment
dba_KCl_Report <- dba.report(dba_KCl, contrast=1, th=1, bUsePval=TRUE, bCounts = TRUE, bFlip = TRUE)


```


```{r}
mygenes <- c("FOS", "NPAS4", "MALAT1", "ERG", "OLIG2", "NR4A1", "HOMER1", "SFI1", "HDAC2", "HNRNPA2B1", "SIRT1", "BDNF", "ARC", "HIC1", "LINC00473", "ZNF331", "ADRA1B")
list <- dba_1Day_EdU_KCl_TTX_ESCin$peaks
RPKMs <- data.frame(list[[1]]$RPKM,list[[2]]$RPKM,list[[3]]$RPKM,list[[4]]$RPKM,list[[5]]$RPKM,list[[6]]$RPKM,list[[7]]$RPKM,list[[8]]$RPKM,list[[9]]$RPKM,list[[10]]$RPKM,list[[11]]$RPKM,list[[12]]$RPKM)

names <- c("H9_EdU_A","H9_EdU_B","H1_TTX_A","H1_TTX_B","H1_EdU_A","H1_EdU_B","H1_KCl_A","H1_KCl_B","H9_TTX_A","H9_TTX_B","H9_KCl_A","H9_KCl_B")
colnames(RPKMs) <- names

bed <- list[[1]][,1:3]
rpkm_bed <- cbind(bed,RPKMs)

rpkm_gr <- makeGRangesFromDataFrame(rpkm_bed, keep.extra.columns = TRUE)
peakAnno_RPKMs <- annotatePeak(rpkm_gr, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakanno_rpkm_df <- data.frame(peakAnno_RPKMs)

#rpkm_promoters <- peakanno_rpkm_df[peakanno_rpkm_df$annotation == 'Promoter (<=1kb)']
rpkm_promoters <- subset(peakanno_rpkm_df, peakanno_rpkm_df$annotation %in% c('Promoter (<=1kb)','Promoter (1-2kb)','Promoter (2-3kb)'))
View(rpkm_promoters)
rpkm_activity_subset <- subset(rpkm_promoters, rpkm_promoters$SYMBOL %in% mygenes)

rpkm_test <- rpkm_promoters

rpkm_test$color <- "Other"
rpkm_test$color[rpkm_promoters$SYMBOL %in% mygenes] <- "MyGenes"


library(dplyr)


test2 <- rpkm_test[,c(6:17,28)]

Promoter_RPKMs <- test2 %>%
group_by(SYMBOL) %>%
summarise_all(sum)

Promoter_RPKMs$color <- "Other"
Promoter_RPKMs$color[Promoter_RPKMs$SYMBOL %in% mygenes] <- "MyGenes"


Promoter_RPKMs$Ctl_avg <-  rowSums(Promoter_RPKMs[,c(2,3,6,7)], na.rm = FALSE, dims = 1)/4
Promoter_RPKMs$KCL_avg <- rowSums(Promoter_RPKMs[,c(8,9,12,13)], na.rm = FALSE, dims = 1)/4
Promoter_RPKMs$TTX_avg <- rowSums(Promoter_RPKMs[,c(4,5,10,11)], na.rm = FALSE, dims = 1)/4
Promoter_RPKMs$delta_TTX <- abs(Promoter_RPKMs$TTX_avg - Promoter_RPKMs$Ctl_avg)
Promoter_RPKMs$delta_KCL <- abs(Promoter_RPKMs$KCL_avg - Promoter_RPKMs$Ctl_avg)

Promoter_RPKMs_TTX <- Promoter_RPKMs[,c(1,14,17)]
Promoter_RPKMs_KCL <- Promoter_RPKMs[,c(1,14,16)]
Promoter_RPKMs_CTL <- Promoter_RPKMs[,c(1,14,15)]
Promoter_RPKMs_deltaTTX <- Promoter_RPKMs[,c(1,14,18)]
Promoter_RPKMs_deltaKCL <- Promoter_RPKMs[,c(1,14,19)]

ggplot(Promoter_RPKMs_TTX, aes(x=color, y=TTX_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs w TTX")

ggplot(Promoter_RPKMs_KCL, aes(x=color, y=KCL_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs w KCL")

ggplot(Promoter_RPKMs_CTL, aes(x=color, y=Ctl_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs Basal")

ggplot(Promoter_RPKMs_deltaTTX, aes(x=color, y=delta_TTX)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color))  + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs change with TTX")

ggplot(Promoter_RPKMs_deltaKCL, aes(x=color, y=delta_KCL)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs change with KCL")

####


rpkm_test2 <- peakanno_rpkm_df

rpkm_test2$color <- "Other"
rpkm_test2$color[rpkm_test2$SYMBOL %in% mygenes] <- "MyGenes"



library(dplyr)


test3 <- rpkm_test2[,c(6:17,28)]

Gene_RPKMs <- test3 %>%
group_by(SYMBOL) %>%
summarise_all(sum)

Gene_RPKMs$color <- "Other"
Gene_RPKMs$color[Gene_RPKMs$SYMBOL %in% mygenes] <- "MyGenes"


Gene_RPKMs$Ctl_avg <-  rowSums(Gene_RPKMs[,c(2,3,6,7)], na.rm = FALSE, dims = 1)/4
Gene_RPKMs$KCL_avg <- rowSums(Gene_RPKMs[,c(8,9,12,13)], na.rm = FALSE, dims = 1)/4
Gene_RPKMs$TTX_avg <- rowSums(Gene_RPKMs[,c(4,5,10,11)], na.rm = FALSE, dims = 1)/4
Gene_RPKMs$delta_TTX <- abs(Gene_RPKMs$TTX_avg - Gene_RPKMs$Ctl_avg)
Gene_RPKMs$delta_KCL <- abs(Gene_RPKMs$KCL_avg - Gene_RPKMs$Ctl_avg)

Gene_RPKM_TTX <- Gene_RPKMs[,c(1,14,17)]
Gene_RPKM_KCL <- Gene_RPKMs[,c(1,14,16)]
Gene_RPKM_CTL <- Gene_RPKMs[,c(1,14,15)]
Gene_RPKMs_deltaTTX <- Gene_RPKMs[,c(1,14,18)]
Gene_RPKMs_deltaKCL <- Gene_RPKMs[,c(1,14,19)]

ggplot(Gene_RPKM_TTX, aes(x=color, y=TTX_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs w TTX")

ggplot(Gene_RPKM_KCL, aes(x=color, y=KCL_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs w KCL")

ggplot(Gene_RPKM_CTL, aes(x=color, y=Ctl_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs Basal")

ggplot(Gene_RPKMs_deltaTTX, aes(x=color, y=delta_TTX)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color))  + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs change with TTX")

ggplot(Gene_RPKMs_deltaKCL, aes(x=color, y=delta_KCL)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs change with KCL")
####

activity_rpkm_t <- data.frame(t(Activity_RPKMs))

Act_RPKM <- Activity_RPKMs[,-1]

rownames(Act_RPKM) <- Activity_RPKMs$SYMBOL
View(Act_RPKM)

activity_rpkm_t <- data.frame(t(Act_RPKM))

activity_rpkm_t$Class <- "bg"
activity_rpkm_t$Class[c(1,2,5,6)] <- "Ctl"
activity_rpkm_t$Class[c(3,4,9,10)] <- "TTX"
activity_rpkm_t$Class[c(7,8,11,12)] <- "KCl"
mdata <- melt(activity_rpkm_t, id=c("Class"))
#mdata2 <- mdata[mdata$Class != "KCL PKi",]

activity_rpkm_t_new <- activity_rpkm_t[activity_rpkm_t$Class !="KCL PKi",]

ggplot(mdata, aes(x=Class, y=value)) + geom_boxplot(aes(x=Class, y=value, fill=Class)) + facet_grid(. ~ variable)  + scale_y_log10() + theme_classic() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90)) + ylab("RPKM") + stat_compare_means(label = "p.signif", method = "t.test",ref.group = "Ctl")



rpkm_promoter_df <- rpkm_promoters[,c(6:17,28)]

Activity_Promtoer_RPKMs <- rpkm_promoter_df %>%
group_by(SYMBOL) %>%
summarise_all(sum)

APR <- Activity_Promtoer_RPKMs[complete.cases(Activity_Promtoer_RPKMs), ]

Act_RPKM <- APR[,-1]

rownames(Act_RPKM) <- APR$SYMBOL
activity_rpkm_t <- data.frame(t(Act_RPKM))
activity_rpkm_t$Class <- "bg"
activity_rpkm_t$Class[c(1,2,5,6)] <- "Ctl"
activity_rpkm_t$Class[c(3,4,9,10)] <- "KCL PKi"
activity_rpkm_t$Class[c(7,8,11,12)] <- "KCl"
mdata <- melt(activity_rpkm_t, id=c("Class"))
mdata2 <- mdata[mdata$Class != "KCL PKi",]

promoter_pvals <- col_t_paired(activity_rpkm_t_new[activity_rpkm_t_new$Class=="Ctl",-18882], activity_rpkm_t_new[activity_rpkm_t_new$Class=="KCl",-18882])
View(promoter_pvals)
promoter_pvals_significant <- promoter_pvals[promoter_pvals$pvalue <= .01,]
write.csv(promoter_pvals_significant, file="promoter_pvals_significant.csv")


gene <- seq2gene(Repair_NOT_ATAC_NOT_H3K27Ac_gr, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego <- enrichGO(gene=rownames(promoter_pvals_significant), OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05, keyType= 'SYMBOL')

pdf("Repair_Only_GeneOntology.pdf")
barplot(ego, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
dev.off()

```

```{r}

dba_EdU_1Day_TTX_low_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("TTX_low","None"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_TTX_low_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_TTX_low_mask, merge="and")
dba_1Day_EdU_TTX_low_ESCin <- dba(DBAobject,dba_EdU_1Day_TTX_low_ESCin_mask)
dba_TTX_low <- dba.contrast(dba_1Day_EdU_TTX_low_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_TTX_low <- dba.analyze(dba_TTX_low, method=DBA_DESEQ2)
#Peaks lost with TTX
dba_TTX_low_Report <- dba.report(dba_TTX_low, contrast=1, th=.05, bUsePval=TRUE, fold=1.5, bGain=TRUE)

dba_EdU_1Day_KCl_KCl.Pki_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("KCl_Pki","KCl"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_KCl_KCl.Pki_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_KCl_KCl.Pki_mask, merge="and")
dba_1Day_EdU_KCl_KCl.Pki_ESCin <- dba(DBAobject,dba_EdU_1Day_KCl_KCl.Pki_ESCin_mask)
dba_KCl_KCl.Pki <- dba.contrast(dba_1Day_EdU_KCl_KCl.Pki_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_KCl_KCl.Pki <- dba.analyze(dba_KCl_KCl.Pki, method=DBA_DESEQ2)
#Peaks lost with KCL + pKi
dba_KCL_KCl.Pki_Report <- dba.report(dba_KCl_KCl.Pki, contrast=1, th=.05, bUsePval=TRUE, fold=1.5, bLoss=TRUE)

dba_EdU_1Day_TTX_low_KCl_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("KCl","TTX_low"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_TTX_low_KCl_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_TTX_low_KCl_mask, merge="and")
dba_1Day_EdU_TTX_low_KCl_ESCin <- dba(DBAobject,dba_EdU_1Day_TTX_low_ESCin_mask)
dba_TTX_low_KCl <- dba.contrast(dba_1Day_EdU_TTX_low_KCl_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_TTX_low_KCl <- dba.analyze(dba_TTX_low_KCl, method=DBA_DESEQ2)
#Peaks lost with TTX
dba_TTX_low_KCl_Report <- dba.report(dba_TTX_low_KCl, contrast=1, th=.05, bUsePval=TRUE, fold=1.5, bGain=TRUE)

dba_EdU_1Day_PARP_mask <- dba.mask(DBAobject,DBA_TREATMENT,c("PARP","None"),mask=dba_EdU_1Day_mask, merge="and")
dba_EdU_1Day_PARP_ESCin_mask <- dba.mask(DBAobject,DBA_TISSUE,"ESC-iN",mask=dba_EdU_1Day_PARP_mask, merge="and")
dba_1Day_EdU_PARP_ESCin <- dba(DBAobject,dba_EdU_1Day_PARP_ESCin_mask)
dba_PARP <- dba.contrast(dba_1Day_EdU_PARP_ESCin, categories=DBA_TREATMENT, minMembers = 2)
dba_PARP <- dba.analyze(dba_PARP, method=DBA_DESEQ2)
#Peaks lost with TTX
dba_PARP_Report <- dba.report(dba_PARP, contrast=1, th=.05, bUsePval=TRUE, fold=1.5)
```

```{r}
dba.plotMA(dba_KCl, bFlip=TRUE)
peakAnno_KCl <- annotatePeak(dba_KCl_Report, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
gene_KCl <- seq2gene(dba_KCl_Report, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego_KCl <- enrichGO(gene=gene_KCl, OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05)
ego_KCl_simp <- simplify(ego_KCl, cutoff = 0.7, by = "p.adjust",select_fun = min)
barplot(ego_KCl, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
barplot(ego_KCl_simp, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
#plotAnnoPie(peakAnno_KCl) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
```


```{r}
dba.plotMA(dba_KCl.Pki, bFlip=TRUE)
peakAnno_KCl.Pki <- annotatePeak(dba_KCl.Pki_Report, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
gene_KCl.Pki <- seq2gene(dba_KCl.Pki_Report, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego_KCl.Pki <- enrichGO(gene=gene_KCl.Pki, OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05)
barplot(ego_KCl.Pki, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
plotAnnoPie(peakAnno_KCl.Pki) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
```

```{r}
dba.plotMA(dba_TTX_low, bFlip=TRUE)
peakAnno_TTX_low <- annotatePeak(dba_TTX_low_Report, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
gene_TTX_low <- seq2gene(dba_TTX_low_Report, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego_TTX_low <- enrichGO(gene=gene_TTX_low, OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05)
barplot(ego_TTX_low, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
plotAnnoPie(peakAnno_TTX_low) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
```

```{r}
dba.plotMA(dba_KCl_KCl.Pki)
peakAnno_KCl_KCl.Pki <- annotatePeak(dba_KCL_KCl.Pki_Report, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
gene_KCl_KCl.Pki <- seq2gene(dba_KCL_KCl.Pki_Report, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego_KCl_KCl.Pki <- enrichGO(gene=gene_KCl_KCl.Pki, OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05)
barplot(ego_KCl_KCl.Pki, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
plotAnnoPie(peakAnno_KCl_KCl.Pki) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
```

```{r}
dba.plotMA(dba_PARP, bFlip=TRUE)
peakAnno_PARP <- annotatePeak(dba_PARP_Report, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
gene_PARP <- seq2gene(dba_PARP_Report, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego_PARP <- enrichGO(gene=gene_PARP, OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05)
barplot(ego_PARP, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
plotAnnoPie(peakAnno_PARP) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))
```


```{r}
dba_Pki_TTX_Intersect <- GenomicRanges::intersect(dba_KCl.Pki_Report,dba_TTX_low_Report)
dba_Pki_TTX_Union <- GenomicRanges::union(dba_KCl.Pki_Report,dba_TTX_low_Report)

peakAnno_Pki_TTX_Intersect <- annotatePeak(dba_Pki_TTX_Intersect, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
gene_Pki_TTX_Intersect <- seq2gene(dba_Pki_TTX_Intersect, tssRegion = c(-1000, 1000), flankDistance = 3000, TxDb=txdb, sameStrand=FALSE)
ego_Pki_TTX_Intersect <- enrichGO(gene=gene_Pki_TTX_Intersect, OrgDb=org.Hs.eg.db, ont="BP", pvalueCutoff =0.05)
barplot(ego_Pki_TTX_Intersect, showCategory=20) + theme_classic() + theme(panel.border = element_rect(colour = "black", fill=NA, size=.5))

```

```{r}
mygenes <- c("ACTB","EGR2","DLX6-AS2","FOS","FOSB","H3F3B","HDAC3","HNRNPA2B1","HOMER2","LINC00461","MALAT1","MIR9-3HG","NPAS4","NR4A1","NR4A3","OLIG2","QKI","RNA45S5","SFI1","SIRT2")
list <- dba_1Day_EdU_KCl_TTX_ESCin$peaks
RPKMs <- data.frame(list[[1]]$RPKM,list[[2]]$RPKM,list[[3]]$RPKM,list[[4]]$RPKM,list[[5]]$RPKM,list[[6]]$RPKM,list[[7]]$RPKM,list[[8]]$RPKM,list[[9]]$RPKM,list[[10]]$RPKM,list[[11]]$RPKM,list[[12]]$RPKM)

names <- c("H9_EdU_A","H9_EdU_B","H1_TTX_A","H1_TTX_B","H1_EdU_A","H1_EdU_B","H1_KCl_A","H1_KCl_B","H9_TTX_A","H9_TTX_B","H9_KCl_A","H9_KCl_B")
colnames(RPKMs) <- names

bed <- list[[1]][,1:3]
rpkm_bed <- cbind(bed,RPKMs)

rpkm_gr <- makeGRangesFromDataFrame(rpkm_bed, keep.extra.columns = TRUE)
peakAnno_RPKMs <- annotatePeak(rpkm_gr, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakanno_rpkm_df <- data.frame(peakAnno_RPKMs)

rpkm_genic <- peakanno_rpkm_df[peakanno_rpkm_df$annotation != "Distal Intergenic",]
#rpkm_promoters <- subset(peakanno_rpkm_df, peakanno_rpkm_df$annotation %in% c('Promoter (<=1kb)','Promoter (1-2kb)','Promoter (2-3kb)'))
rpkm_activity_subset <- subset(rpkm_genic, rpkm_genic$SYMBOL %in% mygenes)

test <- rpkm_activity_subset[,c(6:17,28)]


library(dplyr)

Activity_RPKMs <- test %>%
group_by(SYMBOL) %>%
summarise_all(sum)

activity_rpkm_t <- data.frame(t(Activity_RPKMs))

Act_RPKM <- Activity_RPKMs[,-1]

rownames(Act_RPKM) <- Activity_RPKMs$SYMBOL
View(Act_RPKM)

activity_rpkm_t <- data.frame(t(Act_RPKM))

activity_rpkm_t$Class <- "bg"
activity_rpkm_t$Class[c(1,2,5,6)] <- "Ctl"
activity_rpkm_t$Class[c(3,4,9,10)] <- "TTX"
activity_rpkm_t$Class[c(7,8,11,12)] <- "KCl"
mdata <- melt(activity_rpkm_t, id=c("Class"))
#mdata2 <- mdata[mdata$Class != "KCL PKi",]


ggplot(mdata, aes(x=Class, y=value)) + geom_boxplot(aes(x=Class, y=value, fill=Class)) + facet_grid(. ~ variable)  + scale_y_log10() + theme_classic() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90)) + ylab("RPKM") + stat_compare_means(label = "p.signif", method = "t.test",ref.group = "Ctl")
```

```{r}
mygenes <- c("ACTB","EGR2","DLX6-AS2","FOS","FOSB","H3F3B","HDAC3","HNRNPA2B1","HOMER2","LINC00461","MALAT1","MIR9-3HG","NPAS4","NR4A1","NR4A3","OLIG2","QKI","RNA45S5","SFI1","SIRT2")
list <- dba_1Day_EdU_KCl_TTX_ESCin$peaks
RPKMs <- data.frame(list[[1]]$RPKM,list[[2]]$RPKM,list[[3]]$RPKM,list[[4]]$RPKM,list[[5]]$RPKM,list[[6]]$RPKM,list[[7]]$RPKM,list[[8]]$RPKM,list[[9]]$RPKM,list[[10]]$RPKM,list[[11]]$RPKM,list[[12]]$RPKM)

names <- c("H9_EdU_A","H9_EdU_B","H1_TTX_A","H1_TTX_B","H1_EdU_A","H1_EdU_B","H1_KCl_A","H1_KCl_B","H9_TTX_A","H9_TTX_B","H9_KCl_A","H9_KCl_B")
colnames(RPKMs) <- names

bed <- list[[1]][,1:3]
rpkm_bed <- cbind(bed,RPKMs)

rpkm_gr <- makeGRangesFromDataFrame(rpkm_bed, keep.extra.columns = TRUE)
peakAnno_RPKMs <- annotatePeak(rpkm_gr, tssRegion=c(-3000, 3000),TxDb=txdb, annoDb="org.Hs.eg.db")
peakanno_rpkm_df <- data.frame(peakAnno_RPKMs)

#rpkm_genic <- peakanno_rpkm_df[peakanno_rpkm_df$annotation != "Distal Intergenic",]
rpkm_promoters <- subset(peakanno_rpkm_df, peakanno_rpkm_df$annotation %in% c('Promoter (<=1kb)','Promoter (1-2kb)','Promoter (2-3kb)'))
rpkm_activity_subset <- subset(rpkm_promoters, rpkm_promoters$SYMBOL %in% mygenes)

test <- rpkm_activity_subset[,c(6:17,28)]


library(dplyr)

Activity_RPKMs <- test %>%
group_by(SYMBOL) %>%
summarise_all(sum)

activity_rpkm_t <- data.frame(t(Activity_RPKMs))

Act_RPKM <- Activity_RPKMs[,-1]

rownames(Act_RPKM) <- Activity_RPKMs$SYMBOL
View(Act_RPKM)

activity_rpkm_t <- data.frame(t(Act_RPKM))

activity_rpkm_t$Class <- "bg"
activity_rpkm_t$Class[c(1,2,5,6)] <- "Ctl"
activity_rpkm_t$Class[c(3,4,9,10)] <- "TTX"
activity_rpkm_t$Class[c(7,8,11,12)] <- "KCl"
mdata <- melt(activity_rpkm_t, id=c("Class"))
#mdata2 <- mdata[mdata$Class != "KCL PKi",]


ggplot(mdata, aes(x=Class, y=value)) + geom_boxplot(aes(x=Class, y=value, fill=Class)) + facet_grid(. ~ variable)  + scale_y_log10() + theme_classic() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90)) + ylab("RPKM") + stat_compare_means(label = "p.signif", method = "t.test",ref.group = "Ctl")
```

```{r}
mygenes <- c("FOS", "NPAS4", "MALAT1", "ERG", "OLIG2", "NR4A1", "HOMER1", "SFI1", "HDAC2", "HNRNPA2B1", "SIRT1", "BDNF", "ARC", "HIC1", "LINC00473", "ZNF331", "ADRA1B")


salmon_tpm_activity_subset <- subset(salmon_tpm_activity, salmon_tpm_activity$Symbol %in% mygenes)


library(dplyr)



Gene_TPMs<- salmon_tpm_activity %>%
group_by(Symbol) %>%
summarise_all(sum)



Gene_TPMs$Ctl_avg <-  rowSums(Gene_TPMs[,c(2,3,8,9)], na.rm = FALSE, dims = 1)/4
Gene_TPMs$KCL_avg <- rowSums(Gene_TPMs[,c(4,5,10,11)], na.rm = FALSE, dims = 1)/4
Gene_TPMs$TTX_avg <- rowSums(Gene_TPMs[,c(6,7,12,13)], na.rm = FALSE, dims = 1)/4
Gene_TPMs$delta_TTX <- abs(Gene_TPMs$TTX_avg - Gene_TPMs$Ctl_avg)
Gene_TPMs$delta_KCL <- abs(Gene_TPMs$KCL_avg - Gene_TPMs$Ctl_avg)

Gene_TPMs$color <- "Other"
Gene_TPMs$color[Gene_TPMs$Symbol %in% mygenes] <- "MyGenes"

Gene_TPMs_TTX <- Gene_TPMs[,c(1,16,19)]
Gene_TPMs_TTX_subset <- subset(Gene_TPMs_TTX, Gene_TPMs_TTX$TTX_avg >= 2)


Gene_TPMs_KCL <- Gene_TPMs[,c(1,15,19)]
Gene_TPMs_KCL_subset <- subset(Gene_TPMs_KCL, Gene_TPMs_KCL$KCL_avg >= 2)

Gene_TPMs_CTL <- Gene_TPMs[,c(1,14,19)]
Gene_TPMs_CTL_subset <- subset(Gene_TPMs_CTL, Gene_TPMs_CTL$Ctl_avg >= 2)

Gene_TPMs_deltaTTX <- Gene_TPMs[,c(1,14,17,19)]
Gene_TPMs_deltaTTX_subset <- subset(Gene_TPMs_deltaTTX, Gene_TPMs_deltaTTX$Ctl_avg >= 2)

Gene_TPMs_deltaKCL <- Gene_TPMs[,c(1,14,18,19)]
Gene_TPMs_deltaKCL_subset <- subset(Gene_TPMs_deltaKCL, Gene_TPMs_deltaKCL$Ctl_avg >= 2)


ggplot(Gene_TPMs_TTX_subset, aes(x=color, y=TTX_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Salmon TPMs w TTX")

ggplot(Gene_TPMs_KCL_subset, aes(x=color, y=KCL_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Salmon TPMs w KCL")

ggplot(Gene_TPMs_CTL_subset, aes(x=color, y=Ctl_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Salmon TPMs w Basal")

ggplot(Gene_TPMs_deltaTTX_subset, aes(x=color, y=delta_TTX)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color))  + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Salmon TPMs change with TTX") + scale_y_log10()

ggplot(Gene_TPMs_deltaKCL_subset, aes(x=color, y=delta_KCL)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Salmon TPMs change with KCL") + scale_y_log10()




rownames(Gene_TPMs) <- Gene_TPMs$Symbol

activity_rpkm_t <- data.frame(t(Gene_TPMs[,-1]))

activity_rpkm_t$Class <- "bg"
activity_rpkm_t$Class[c(1,2,7,8)] <- "Ctl"
activity_rpkm_t$Class[c(5,6,11,12)] <- "TTX"
activity_rpkm_t$Class[c(3,4,9,10)] <- "KCl"
mdata <- melt(activity_rpkm_t, id=c("Class"))
#mdata2 <- mdata[mdata$Class != "KCL PKi",]

activity_rpkm_t_new <- activity_rpkm_t[activity_rpkm_t$Class !="KCL PKi",]

ggplot(mdata, aes(x=Class, y=value)) + geom_boxplot(aes(x=Class, y=value, fill=Class)) + facet_grid(. ~ variable)  + scale_y_log10() + theme_classic() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90)) + ylab("RPKM") + stat_compare_means(label = "p.signif", method = "t.test",ref.group = "Ctl")

Promoter_RPKMs_TTX <- Promoter_RPKMs[,c(1,14,17)]
Promoter_RPKMs_KCL <- Promoter_RPKMs[,c(1,14,16)]
Promoter_RPKMs_CTL <- Promoter_RPKMs[,c(1,14,15)]
Promoter_RPKMs_deltaTTX <- Promoter_RPKMs[,c(1,14,18)]
Promoter_RPKMs_deltaKCL <- Promoter_RPKMs[,c(1,14,19)]

ggplot(Promoter_RPKMs_TTX, aes(x=color, y=TTX_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs w TTX")

ggplot(Promoter_RPKMs_KCL, aes(x=color, y=KCL_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs w KCL")

ggplot(Promoter_RPKMs_CTL, aes(x=color, y=Ctl_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs Basal")

ggplot(Promoter_RPKMs_deltaTTX, aes(x=color, y=delta_TTX)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color))  + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs change with TTX")

ggplot(Promoter_RPKMs_deltaKCL, aes(x=color, y=delta_KCL)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Promoter RPKMs change with KCL")

####


rpkm_test2 <- peakanno_rpkm_df

rpkm_test2$color <- "Other"
rpkm_test2$color[rpkm_test2$SYMBOL %in% mygenes] <- "MyGenes"



library(dplyr)


test3 <- rpkm_test2[,c(6:17,28)]

Gene_RPKMs <- test3 %>%
group_by(SYMBOL) %>%
summarise_all(sum)

Gene_RPKMs$color <- "Other"
Gene_RPKMs$color[Gene_RPKMs$SYMBOL %in% mygenes] <- "MyGenes"


Gene_RPKMs$Ctl_avg <-  rowSums(Gene_RPKMs[,c(2,3,6,7)], na.rm = FALSE, dims = 1)/4
Gene_RPKMs$KCL_avg <- rowSums(Gene_RPKMs[,c(8,9,12,13)], na.rm = FALSE, dims = 1)/4
Gene_RPKMs$TTX_avg <- rowSums(Gene_RPKMs[,c(4,5,10,11)], na.rm = FALSE, dims = 1)/4
Gene_RPKMs$delta_TTX <- abs(Gene_RPKMs$TTX_avg - Gene_RPKMs$Ctl_avg)
Gene_RPKMs$delta_KCL <- abs(Gene_RPKMs$KCL_avg - Gene_RPKMs$Ctl_avg)

Gene_RPKM_TTX <- Gene_RPKMs[,c(1,14,17)]
Gene_RPKM_KCL <- Gene_RPKMs[,c(1,14,16)]
Gene_RPKM_CTL <- Gene_RPKMs[,c(1,14,15)]
Gene_RPKMs_deltaTTX <- Gene_RPKMs[,c(1,14,18)]
Gene_RPKMs_deltaKCL <- Gene_RPKMs[,c(1,14,19)]

ggplot(Gene_RPKM_TTX, aes(x=color, y=TTX_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs w TTX")

ggplot(Gene_RPKM_KCL, aes(x=color, y=KCL_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs w KCL")

ggplot(Gene_RPKM_CTL, aes(x=color, y=Ctl_avg)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + scale_y_log10() + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs Basal")

ggplot(Gene_RPKMs_deltaTTX, aes(x=color, y=delta_TTX)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color))  + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs change with TTX")

ggplot(Gene_RPKMs_deltaKCL, aes(x=color, y=delta_KCL)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2), aes(colour = color)) + stat_compare_means(label = "p.signif", method = "t.test") + theme_classic() + ggtitle("Gene RPKMs change with KCL")
####

activity_rpkm_t <- data.frame(t(Activity_RPKMs))

Act_RPKM <- Activity_RPKMs[,-1]

rownames(Act_RPKM) <- Activity_RPKMs$SYMBOL
View(Act_RPKM)

activity_rpkm_t <- data.frame(t(Act_RPKM))

activity_rpkm_t$Class <- "bg"
activity_rpkm_t$Class[c(1,2,5,6)] <- "Ctl"
activity_rpkm_t$Class[c(3,4,9,10)] <- "TTX"
activity_rpkm_t$Class[c(7,8,11,12)] <- "KCl"
mdata <- melt(activity_rpkm_t, id=c("Class"))
#mdata2 <- mdata[mdata$Class != "KCL PKi",]

activity_rpkm_t_new <- activity_rpkm_t[activity_rpkm_t$Class !="KCL PKi",]

ggplot(mdata, aes(x=Class, y=value)) + geom_boxplot(aes(x=Class, y=value, fill=Class)) + facet_grid(. ~ variable)  + scale_y_log10() + theme_classic() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90)) + ylab("RPKM") + stat_compare_means(label = "p.signif", method = "t.test",ref.group = "Ctl")